A new tidy data structure to support exploration and modeling of temporal data

### 2019-08-26 reviews/response.Rmd

Along with these major changes, we have done lots of minor tweaks to improve the manuscript.

# Reviewer 1 comments {-}

> More mini examples embeded throughout the manuscript. Mainly it didn't showcase to me tsibble's capability well enough but understandably this may make the manuscript long and may be better left to vignettes.

Thanks for this comment. We have decided to mostly leave these to the vignettes, which are readily available on the web page for the package. The reason for doing this is that we feel that having many mini examples interrupts the flow of the paper. We have made two additions, though, which hopefully address these comments.

A new code snippet (featuring new `pedestrian` dataset) is added to subsection 4.4. This is new part added to the paper, summarising the transformation and modeling parts of the data pipeline section.  A new example is added that showcases how tsibble provides a platform to forecasting. It shows an energy consumption case study, illustrating the cleaner, and more expressive, temporal data modeling pipeline.

@@

> Figure 11 with missing data was a great demonstration for tsibble and the data times series pipeline shown in Figure 3. It may be helpful to reduce the opacity of the points as there is a lot of overplotting. The top line which lumps a number of customers together is not particularly informative here. Perhaps it is better replaced with a histogram.

TODO.

> Authors may like to add/change `spread`/`gather` verbs to `pivot_longer`/`pivot_wider` with the recent move to deprecate the former in tidyr. Likewise authors may like to consider to replace “long data” to “longer data” and “wide data” to “wider data” as long/wide implies absolute terms. <https://tidyr.tidyverse.org/dev/articles/pivot.html>

We'd like to upgrade `spread`/`gather` verbs to `pivot_longer`/`pivot_wider`. But they are not S3 generics yet, which delays the implementation. Conceptually the newly melted columns will be added to the key specification.

@@

> Manuscript does implicitly feel more time series data oriented rather than a general temporal data. E.g. references of time points as index seems inherent from other time series data infrastructure (i.e. zoo and xts) and the presented case studies is not representative of any longitudinal study. This does not mean it should be changed but index to me was not as intuitive to be the temporal variable.

[TODO]

Time indexes lay the contextual foundation to both time series and longitudinal data. `zoo` and `xts` store indices as metadata due the matrix structure, but tsibble's indices are explicitly a data column that can be manipulated. The index may be a date-time varible, as is usual in time series, but could be as simple as an ordered integer as is common in longitudinal data. It is also customizable to any variable that can be ordered. We have made this clearer in Section 3.1 where index specification is explained.

Tsibble is aimed at general temporal data, to unify **data** structures underlying time series and longitudinal problems. In Section 4 of the revised manuscript, we clarify the different focuses of time series and longitudinal **analysis** and modelling. However, we have kept the emphasis on time series for the examples, because there are more functions available for time series model building on tsibble.

### 2019-08-26 tsibble.Rmd
adjusted figures

```{r count-gaps, fig.height = 7, fig.cap = "(ref:count-gaps-cap)"}
```

(ref:count-gaps-cap) Time gap plots for the 49 customers with most implicit missing values, and the remaining customers grouped into the one line at top. Each cross represents an observation missing in time and a line between two dots shows continuous missingness over time. Each row corresponds to one customer. Missing values occur at various times, with more in January and February than other months.

@@

Lastly, a common practice in the energy sector is load forecasting. Forecasting the demand for the last day of 2013 is undertaken, holding the original energy data as the validation set. The most recent December data is fitted by ARIMA models with and without temperature information using automatic order selection [@autoarima]. The logarithmic transformation is applied to the average demand to ensure the positive forecasts. Figure \@ref(fig:elec-forecast) plots the one-day forecasts obtained from both models against the actual demand within the last week window. ARIMA regressed by average temperatures gives a better fit than the one without, although both tend to underestimate the night demand. The forecasting performance is reported in Table \@ref(tab:elec-accuracy), consistent with the findings in Figure \@ref(fig:elec-forecast).

>>>>

```{r count-gaps, fig.height = 8, fig.cap = "(ref:count-gaps-cap)"}
```

(ref:count-gaps-cap) Time gap plots for the 49 customers with most implicit missing values, and the remaining customers grouped into the one line at the bottom panel. Each cross represents an observation missing in time and a line between two dots shows continuous missingness over time. Each row corresponds to one customer. Missing values occur at various times, with more in January and February than other months.

@@

Lastly, a common practice in the energy sector is load forecasting. Forecasting the demand for the last day of 2013 is undertaken, holding the original energy data as the validation set. The most recent December data is fitted by ARIMA models with and without temperature information using automatic order selection [@autoarima]. The logarithmic transformation is applied to the average demand to ensure the positive forecasts. Figure \@ref(fig:elec-forecast) plots the one-day forecasts obtained from both models against the actual demand within the last two-week window. ARIMA regressed by average temperatures gives a better fit than the one without, although both tend to underestimate the night demand. The forecasting performance is reported in Table \@ref(tab:elec-accuracy), consistent with the findings in Figure \@ref(fig:elec-forecast).
